Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-28 draft.tex
small changes in HKR section

This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $\EE_n$ algebras.
(The classic theorem proves the $n=1$ situation.)
Such a result is proved by very different methods in~\cite{CalWil}.
Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.

Our approach applies only to a certain class of dg commutative algebras,
due to a technical hypothesis necessary to apply our methods.
We need as input an augmented dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
In other words, we want to know that the generators can be realized as the graded linear dual of some other graded vector space.
We say such an $A$ is of {\em type~($\star$)}.

\begin{prp}
Let $A$ be an augmented dg commutative algebra of type~($\star$).
Then 
\[
{\frak Z}_n(A) \simeq {\rm Poly}_n(A) \simeq \Sym_A(\TT_A[-n]).
\]
\end{prp}

\owen{This proposition should be phrased correctly. The RHS isn't quite correct unless $A$ is good enough.}

\begin{proof}
\owen{The method described in the email.}
\end{proof}

@@

Let $\fg_S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
\begin{align*}
\Omega^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
\Omega_c^\bu(V) \otimes \fg_S &\xto{\simeq} \Omega_c^\bu(V \times S) \otimes \fg 
\end{align*}
and hence a quasi-isomorphism
\[
\bU_k \fg_S \xto{\simeq} \int_S \bU_n \fg
\]
of factorization algebras.

Likewise, on each open set $V \subset \RR^k$, 
we obtain a quasi-isomorphism
\[
\bZ_k(\fg_S)(V) \cong \clies( \Omega^\bu(V) \otimes \fg_S, \bU_k \fg_S) \xto{\simeq} \clies(\Omega^\bu(V \times S) \otimes \fg, \bU_n(V \times S))
\]
and this map is functorial in opens.
The righthand side is, however, the pushforward $\int_S \bZ_n \fg$.
\owen{That map is not the canonical map as it goes the ``wrong way,'' but I'm pretty sure it provides the inverse-up-to-qiso we need.}
\end{proof}

>>>>

This result is the simplest case of a generalized Hochschild-Kostant-Rosenberg theorem for commutative algebras viewed as $\EE_n$ algebras.
(The classic theorem proves the $n=1$ situation.)
Such a result is proved by very different methods in~\cite{CalWil, ToenBranes}.
Now we swiftly describe how to use methods like those in this paper to prove a version of this powerful result.

\owen{Greg, please read this below.}
First, we wish to define ${\rm Poly}_n(A)$ for an arbitrary dg commutative algebra $A$ in a way that gives the ``correct'' derived answer, i.e., the answer up to quasi-isomorphism of dg commutative algebras.
Concretely, one should replace $A$ by a quasi-isomorphic but better behaved algebra $\widetilde{A}$, 
such as semi-free resolution or cofibrant replacement with respect to some nice model category structure.
Then one computes the tangent complex $\TT_{\widetilde{A}}$, i.e., the derived derivations.
The {\em shifted polyvector fields} of $A$ means
\[
{\rm Poly}_n(A) \simeq \Sym_{\widetilde{A}} (\TT_{\widetilde{A}}[1-n]),
\]
which is again a dg commutative algebra up to quasi-isomorphism.

Second, we introduce a technical hypothesis  needed to apply our methods.
We need an {\em augmented} dg commutative algebra $\epsilon: A \to k$ that admits a semifree resolution of the form $(\Sym(V^\vee), \partial)$, where $V$ is some graded vector space.
In other words, we need that the generators can be realized as the graded linear dual of some other graded vector space.
We say such an algebra $A$ is of {\em type~($\star$)}.

\begin{prp}
Let $A$ be an augmented dg commutative algebra of type~($\star$).
Then 
\[
{\frak Z}_n(A) \simeq {\rm Poly}_n(A).
\]
\end{prp}

\begin{proof}
By our technical hypothesis, we are free to replace $A$ by a semifree resolution $(\Sym(V^\vee), \partial)$. 
Ignoring the differential, we see that our situation resembles our central result for an abelian Lie algebra,
and so we now mimic the proof of our central result.

There is a natural homotopy-locally constant sheaf of cochain complexes $\Omega^* \otimes V$ with differential $\d_{dR} + \partial$,
which is a soft replacement for the locally constant sheaf $V$.
Define the factorization algebra 
\[
F_A = (\Sym((\Omega* \otimes V)* ), \d_{dR} + \partial) 
\]
which is manifestly commutative and is quasi-isomorphic to $A$ on every disk.
Hence $F_A$ is a commutative, locally constant factorization algebra that models~$A$.

\owen{I'm partway done.}

3) Define the putative center as a factorization algebra by starting with the polyvector fields for this semifree resolution

4) Show this putative center fits into the commuting triangle and hence possesses a canonical map to the "true" center

5) Use the Francis-Lurie recognition principle to show this map is a quasi-iso
\end{proof}

@@

Let $\fg^S$ denote the $L_\infty$ algebra $\Omega^\bu(S) \otimes \fg$. 
Then these quasi-isomorphisms above imply there are quasi-isomorphisms of $L_\infty$ algebras
\begin{align*}
\Omega^\bu(V) \otimes \fg^S &\xto{\simeq} \Omega^\bu(V \times S) \otimes \fg \\
\Omega_c^\bu(V) \otimes \fg^S &\xto{\simeq} \Omega_c^\bu(V \times S) \otimes \fg 
\end{align*}
and hence a quasi-isomorphism
\[
\bU_k \left(\fg^S\right) \xto{\simeq} \int_S \bU_n \fg
\]
of factorization algebras.

\owen{The following does not make sense. An injective quasi-isomorphism of dg vector spaces does not induce a map of endomorphisms on the nose. But they are canonically quasi-isomorphic by a zigzag.}
Likewise, on each open set $V \subset \RR^k$, 
we obtain a quasi-isomorphism
\[
\bZ_k(\fg^S)(V) \cong \clies( \Omega^\bu(V) \otimes \fg^S, \bU_k \left(\fg^S\right)) \xto{\simeq} \clies(\Omega^\bu(V \times S) \otimes \fg, \bU_n(V \times S))
\]
and this map is functorial in opens.
The righthand side is, however, the pushforward $\int_S \bZ_n \fg$.
\end{proof}
